%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Based on IEEE the conference template available                     %
% at https://www.ieee.org/conferences/publishing/templates.html       %
% Adapted for the Data Science Lab course at Politecnico di Torino    %
% by Giuseppe Attanasio, Flavio Giobergia                             %
% 2020, DataBase and Data Mining Group                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}


\begin{document}

\title{Estimating the age of people from vocal recordings}

\author{\IEEEauthorblockN{ Bello Renato}
\IEEEauthorblockA{\textit{Politecnico di Torino} \\
Student id: s341965 \\
s341965@studenti.polito.it}
\and
\IEEEauthorblockN{Chiodo Martina}
\IEEEauthorblockA{\textit{Politecnico di Torino} \\
Student id: s343310 \\
s343310@studenti.polito.it}
}

\maketitle

\begin{abstract}
In this report we tried to solve a regression problem, the goal is to estimate the age of a person from a vocal recording. We used both the csv dataset and the vocal recording to extract all the features needed to make the regression.
\end{abstract}

\section{Problem overview}
% Here you should describe your problem
\input{chap/prob_overview.tex}

\section{Proposed approach}
% In this section, you will present your solution. Please fill in accordingly.
\subsection{Preprocessing}
\input{chap/preprocessing.tex}
\subsection{Model selection}
\input{chap/modelselection.tex}
\subsection{Hyperparameter tuning}
\input{chap/hypertuning.tex}



\section{Results}
% Here you will present your results (models \& configurations selected, performance achieved)
\input{chap/results.tex}

\section{Discussion}
The proposed approach obtains results that
outperform, even if not by much, the naive baseline defined. We have empirically shown that the selected regressors perform similarly for this specific task, achieving satisfactory results in terms of RMSE.
 
However, we acknowledge that the results obtained from the regressors were not so accurate, this inefficiency arises from the fact that the target value is not well distributed, as shown in Figure \ref{hist_distributivi}. As a result, prediction for bigger values of age are not as precise as prediction for lower values of age, as shown by looking the residuals in Figures \ref{fig:res_Ridge} and \ref{fig:res_MLP}. It is highly likely that, using a dataset that is less imbalanced in the target variable, the results would be better. 

An other idea for computing better results was splitting the dataset by the gender, in fact the voice is different for different genders. We tried to train two regressors, one for male and the other for female gender, however, the results were suboptimal. This type of strategy would have been successful if the dataset had been more complete.


% Any relevant discussion goes here.
\input{chap/discussions.tex}


\bibliography{bibliography}
\bibliographystyle{ieeetr}

\end{document}
